Simple simulations for a simplified version of web-boost-2

### 2020-07-21 analysis/simulation_simpleveb-boost2.Rmd
FBM workflow

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mr.ash.alpha)
source("~/causalTWAS/causal-TWAS/code/fit_mr.ash.R")
source("~/causalTWAS/causal-TWAS/code/mr.ash2.R")
```

@@

```{r run mr.ash}
fit <- mr.ash(X, y, method="caisa")
summary_mr.ash(fit)

@@

@@

```{r run mr.ash2, gene}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.gene, X.SNP, y)

print("for gene effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```

@@

```{r run mr.ash2, snp}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.SNP, X.gene, y)

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit2$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit1$beta, main = "beta for SNP effect")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F)
library(mr.ash.alpha)
library(biglasso)
library(bigmemory)
library(bigstatsr)
source("~/causalTWAS/causal-TWAS/code/fit_mr.ash.R")
source("~/causalTWAS/causal-TWAS/code/mr.ash2.R")
```

@@

```{r run mr.ash}
myorder <- 1:dim(X)[2]
myorder[gene.idx] <- 1:length(gene.idx)
myorder[SNP.idx] <- (length(gene.idx) + 1): length(myorder)

X <- cbind(X[, gene.idx], X[, SNP.idx])
fit <- mr.ash(X, y, method="caisa", update.order = NULL)
summary_mr.ash(fit)

@@

```{r run mr.ash}
myorder <- 1:dim(X)[2]
myorder[gene.idx] <- (length(SNP.idx) + 1): length(myorder)
myorder[SNP.idx] <- 1:length(SNP.idx)
X <- cbind(X[,SNP.idx], X[,gene.idx])
fit2 <- mr.ash(X, y, method="caisa", update.order = NULL)
summary_mr.ash(fit2)

plot_beta(beta[gene.idx], fit2$beta[gene.idx], main = "beta for gene effect")
plot_beta(beta[SNP.idx], fit2$beta[SNP.idx], main = "beta for SNP effect")
```

@@

```{r run mr.ash2, gene}
X.gene <- X[, gene.idx]
X.SNP <- as_FBM(X[, SNP.idx])
fit <- mr.ash2s(X.gene, X.SNP, y, init.order = "expr-snp")

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```

@@

```{r run mr.ash2, snp}
fit <- mr.ash2s(X.gene, X.SNP, y, init.order = "snp-expr")

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```

### init with lasso

```{r run mr.ash2, lasso}
fit <- mr.ash2s(X.gene, X.SNP, y, mr.ash.init = "lasso")

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```

### init with lasso SNP

```{r run mr.ash2, lassosnp}
fit <- mr.ash2s( X.gene, X.SNP, y, mr.ash.init = "lassoSNP")

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```
